A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
Bib changes
summary table for turker quality

%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
\begin{figure}[h]
\footnotesize
\begin{tabular}{lrlrlr}\hline\hline
%Language&\# Turkers\\
\hline
English&591&	French&63&	Vietnamese&34\\
Tamil&253&	Polish&61&	Macedonian&31\\
Malayalam&219&	Urdu&56&	Cebuano&29\\
Hindi&149&	Tagalog&54&	Swedish&26\\
Spanish&131&	Marathi&48&	Bulgarian&25\\
Telugu&87&	Russian&44&	Hungarian&23\\
Chinese&86&	Italian&43&	Swahili&23\\
Romanian&85&	Bengali&41&	Thai&22\\
Portuguese&82&	Gujarati&39&	Catalan&22\\
Arabic&74&	Hebrew&38&	Lithuanian&21\\
Kannada&72&	Dutch&37&	Punjabi&21\\
German&66&	Turkish&35&	Others &$\leq$20\\
\hline\hline
\end{tabular}
\normalsize
\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 langs with $\leq$20 speakers  each for a total of 423 remaining speakers.  We omit Turkers did not self-report their native languages (1,801), 243 who reported two native languages, 83 who reported $\geq$3 native languages.}\label{lang-pie}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Several reports examine Mechanical Turk as an economic market \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently, it has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries \cite{AmazonRequesterTour}.  This suggest that its worker population that should represent a diverse set of languages.

@@

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{table*}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English] your native language? &129,049\\
How many years have you spoken [HIT language]?&159,807\\
How many years have you spoken English?&159,808\\
What country do you live in?&329,033\\
Current location (collected automatically)& 329,033\\
\hline\\
Total assignments& 329,033\\
Total unique workers& 6,034\\
\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of assignments with valid responses for each}
\label{survey-tab}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
%%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
%\begin{figure}[h]
%\centering
%\includegraphics[width=\linewidth]{figures/natlang-pie}
%\caption{Self-reported native language of 3,154 bilingual Turkers.  Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
%\label{lang-pie}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Survey Design}
The central task in this study was to use Mechanical Turk to create bilingual dictionaries for over 100 languages in order to test Mechanical Turk's bilingual population.

@@

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\centering
\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
\caption{Time (in days) to complete all HITs in each language. Red bar shows time until first HIT was started,
% relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
 blue bar shows time until all HITs in each language were completed.}
\label{completion-time}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
\begin{figure}[h]
\footnotesize
\begin{tabular}{lrlrlr}\hline\hline
%Language&\# Turkers\\
\hline
English&591&	French&63&	Vietnamese&34\\
Tamil&253&	Polish&61&	Macedonian&31\\
Malayalam&219&	Urdu&56&	Cebuano&29\\
Hindi&149&	Tagalog&54&	Swedish&26\\
Spanish&131&	Marathi&48&	Bulgarian&25\\
Telugu&87&	Russian&44&	Hungarian&23\\
Chinese&86&	Italian&43&	Swahili&23\\
Romanian&85&	Bengali&41&	Thai&22\\
Portuguese&82&	Gujarati&39&	Catalan&22\\
Arabic&74&	Hebrew&38&	Lithuanian&21\\
Kannada&72&	Dutch&37&	Punjabi&21\\
German&66&	Turkish&35&	Others &$\leq$20\\
\hline\hline
\end{tabular}
\normalsize
\caption{XXX}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/completiontime}
\caption{Time (in days) to complete all HITs in each language. Red bar shows time until first HIT was started, relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). Blue bar shows time until all HITs in each language were completed.}
\label{completion-time}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Several reports examine Mechanical Turk as an economic market \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently, it has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries \cite{AmazonRequesterTour}.  This suggests that its worker population should represent a diverse set of languages.

@@

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{table*}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English] your native language? &NUM\\
How many years have you spoken [HIT language]?&NUM\\
How many years have you spoken English?&NUM\\
What country do you live in?&308,079\\
Current location (collected automatically)& 308,079\\
\hline\\
Total assignments& 308,079\\
Total unique workers& 5,271\\
\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of assignments with valid responses for each}
\label{survey-tab}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{figures/natlang-pie}
\caption{Self-reported native language of 3,154 bilingual Turkers.  Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
\label{lang-pie}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Survey Design}
The central task in this study was to use Mechanical Turk to create bilingual dictionaries for over 100 languages in order to test Mechanical Turk's bilingual population.

@@

### 2013-02-20 writeup/summary.tex
summary table for turker quality

\begin{figure}[h]
\centering
*** PLACE HOLDER NUMBERS; NUMBERS WITH ACCPETED HITS ONLY STILL RUNNING ***
\begin{tabular}{llcccccc}
\multicolumn{8}{c}{Number of Turkers per language}\\
\hline\hline
&&Total \# Turkers&\multicolumn{2}{c}{\# Turkers in language region}&\multicolumn{2}{c}{Avg. Turker quality (Dictionary size)}\\
&&&Overall&By country&In region&Out of region\\
\hline\hline
hi&Hindi&312&300&India (285) Uae (5) &\textbf{0.5387} (9908)&0.4728 (41) \\
&&&&Scotland (5) Other (5) &&&\\
&&&&&&&\\
ta&Tamil&294&278&India (271) US (3) &\textbf{0.5528} (9974)&0.54 (5) \\
&&&&Canada (2) Other (2) &&&\\
&&&&&&&\\
ml&Malayalam&245&235&India (224) Uae (6) &0.4759 (9966)&\textbf{0.5523} (25)\\
&&&&US (3) Other (2) &&&\\
&&&&&&&\\
es&Spanish&235&206&US (131) Mexico (18) &\textbf{0.2711} (9768)&0.2677 (67) \\
&&&&Westspain (14) Other (43) &&&\\
&&&&&&&\\
fr&French&202&183&India (68) US (48) &0.2907 (9514)&\textbf{0.3063} (386)\\
&&&&France (25) Other (42) &&&\\
&&&&&&&\\
de&German&163&100&Germany (51) US (29) &\textbf{0.3527} (8892)&0.306 (1029) \\
&&&&Austria (9) Other (11) &&&\\
&&&&&&&\\
it&Italian&159&98&Italy (44) US (32) &\textbf{0.3221} (7885)&0.2734 (1870) \\
&&&&Romania (9) Other (13) &&&\\
&&&&&&&\\
zh&Chinese&150&130&US (80) Singapore (15) &0.1821 (3510)&\textbf{0.4113} (137)\\
&&&&China (14) Other (21) &&&\\
&&&&&&&\\
ms&Malay&128&15&Malaysia (8) Singapore (4) &\textbf{0.2946} (6147)&0.2755 (3619) \\
&&&&US (2) Other (1) &&&\\
&&&&&&&\\
ga&Irish&121&58&US (41) Ireland (13) &\textbf{0.3201} (3775)&0.2612 (6139) \\
&&&&Scotland (4) &&&\\
&&&&&&&\\
\hline\hline
\end{tabular}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\begin{tabular}{llcccccc}
\multicolumn{8}{c}{Number of Turkers per language}\\
\hline\hline
&&Total \# Turkers&\multicolumn{2}{c}{\# Turkers in language region}&\multicolumn{2}{c}{Avg. Turker quality}\\
&&&Overall&By country&In region&Out of region\\
\hline\hline
hi&Hindi&362&299&India (285) Uae (5) &\textbf{0.5395}&0.474\\
&&&&Uk (5) Other (5) &&&\\
&&&&&&&\\
ta&Tamil&304&278&India (271) US (3) &\textbf{0.5528}&0.54\\
&&&&Canada (2) Other (2) &&&\\
&&&&&&&\\
ml&Malayalam&284&235&India (224) Uae (6) &0.4759&\textbf{0.5523}\\
&&&&US (3) Other (2) &&&\\
&&&&&&&\\
es&Spanish&244&205&US (131) Mexico (18) &\textbf{0.2723}&0.2675\\
&&&&Westspain (14) Other (43) &&&\\
&&&&&&&\\
fr&French&217&183&India (68) US (48) &0.2907&\textbf{0.307}\\
&&&&France (25) Other (42) &&&\\
&&&&&&&\\
de&German&170&99&Germany (51) US (29) &\textbf{0.3529}&0.306\\
&&&&Austria (9) Other (11) &&&\\
&&&&&&&\\
it&Italian&166&98&Italy (44) US (32) &\textbf{0.3223}&0.2733\\
&&&&Romania (9) Other (13) &&&\\
&&&&&&&\\
zh&Chinese&151&123&US (80) Singapore (15) &\textbf{0.4171}&0.4123\\
&&&&China (14) Other (21) &&&\\
&&&&&&&\\
te&Telugu&137&102&India (98) US (3) &\textbf{0.4793}&0.4051\\
&&&&Uae (1) &&&\\
&&&&&&&\\
ms&Malay&131&15&Malaysia (8) Singapore (4) &\textbf{0.2964}&0.276\\
&&&&US (2) Other (1) &&&\\
&&&&&&&\\
\hline\hline
\end{tabular}
\end{figure}
